Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-05-08 paper.tex
Superscript
Highlight a sentence which is hard to understand

@@

Our implementation provides a predefined right triangle pattern where arguments
of a correlation function $x_1$ and $x_2$ are fixed to be parallel to one of the
axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern})
\cite{dimitrakopoulos2010high}. The output has dimensions $D_1 \times D_2$ where
$D_1$ and $D_2$ are dimensions of the input array along selected axes. Note that
shift operators with such $x_1$ and $x_2$ represent a 3-point function computed
within a 3D domain, but along a predefined direction (see below).
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\linewidth]{images/pattern.png}
  \caption[]{The pattern used for calculation of $S_3$ function in our
    implementation.}
  \label{fig:pattern}
\end{figure}

>>>>

When a phase of interest is clear from the context or irrelavant a superscript
can be omitted from mathematical notation of correlation functions.

@@

Our implementation provides a predefined right triangle pattern where arguments
of a correlation function $x_1$ and $x_2$ are fixed to be parallel to one of the
axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern})
\cite{dimitrakopoulos2010high}. The output has dimensions $D_1 \times D_2$ where
$D_1$ and $D_2$ are dimensions of the input array along selected axes.
\highlight{I CANNOT UNDESTAND THIS SENTENCE: Note that shift operators with such
  $x_1$ and $x_2$ represent a 3-point function computed within a 3D domain, but
  along a predefined direction (see below).}
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\linewidth]{images/pattern.png}
  \caption[]{The pattern used for calculation of $S_3$ function in our
    implementation.}
  \label{fig:pattern}
\end{figure}
